The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-14 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

\emph{separate winning percentage from the other comparisons. Use
fisher.test for it}

Tests for differences in proportions were conducted for comparing winning percentage
and the three different shooting percentages in 2020 to those of
2017-2019. The null hypothesis is 
\[
H_0: p_1 = p_2,
\]
where $p_1$ and $p_2$ are the shooting percentage in 2020 and
2017-2019, respectively. Or $p_1$ and $p_2$ are the home winning percentage for 2020 and
2017-2019, respectively. This proportion comes from summing the number of home teams wins
and dividing by the total number of games played.
$\hat{p}_1$ represents sample proportion for 2020 and $\hat{p}_2$ represents sample
proportion for 2017-2019. The test statistic is
where $\hat p$ is the pooled shooting percentage of 2017-2020. Or where $\hat p$ is the 
pooled home team winning percentage of 2017-2020.
The null distribution of the test statistic is also standard normal.
The test will be conducted seven times, once comparing home winning percentage for 
2020 to that of 2017-2019 and once for each of two-point shooting, three-point shooting and
free throws for both home and away teams in 2020 vs. 2017-2019. These hypotheses will also be
tested using both a z-test and a nonparametric test. The Wilcoxon test will be used for shooting percentages and
Fisher's test will be used to test the binary variable of home team winning.

>>>>

Tests for differences in proportions was conducted for comparing winning percentage of 
home teams in 2020 to those of 2017-2019. The null hypothesis is 
\[
H_0: p_1 = p_2,
\]
where $p_1$ and $p_2$ are the home winning percentage for 2020 and
2017-2019, respectively. $\hat{p}_1$ represents sample proportion for 2020 and $\hat{p}_2$ represents sample
proportion for 2017-2019. This proportion comes from summing the number of home teams wins
and dividing by the total number of games played. The test statistic is where $\hat p$ is the 
pooled home team winning percentage of 2017-2020. The null distribution of the test statistic is also standard normal.
This hypothesis will be tested using both a z-test and Fisher's test. Fisher's test is preferred, like Wilcoxon, 
because it is distribution free.

Tests for differences in proportions were also conducted for comparing shooting percentage on 
two-pointers, three-pointers and free throws for home and away teams in 2020 to those of 2017-2019. 
The null hypothesis is 
\[
H_0: p_1 = p_2,
\]
where $p_1$ and $p_2$ are the shooting percentage in 2020 and
2017-2019, respectively. $\hat{p}_1$ represents sample proportion for 2020 and $\hat{p}_2$ represents sample
proportion for 2017-2019. The test statistic is
where $\hat p$ is the pooled shooting percentage of 2017-2020.
The null distribution of the test statistic is also standard normal.
The test will be conducted six times, once for each of two-point shooting, three-point shooting and
free throws for both home and away teams in 2020 vs. 2017-2019. These hypotheses will also be
tested using both a z-test and the nonparametric Wilcoxon test.
